\documentclass[11pt, a4paper]{article}

\usepackage{cite}

\usepackage{booktabs}
\usepackage{siunitx}
\DeclareSIUnit{\calorie}{cal}

\usepackage{pgfplots}
\usepackage{pgfplotstable}
\pgfplotsset{compat=newest}

\usepackage{physics}

\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{positioning, calc}

\pgfmathsetmacro{\s}{0.5}
\pgfmathsetmacro{\r}{0.5cm}

\usepackage[caption=false]{subfig}


\title{Predicting the binding free energy of DNA intercalators}
\author{Kristof Farkas-Pall}

\begin{document}

% \maketitle

\section*{Abstract}

Planar aromatic molecules can interact with DNA chains by intercalating between consecutive basepairs. Once intercalated they can cause mutations during gene expression resulting in cancerous cells. This same mechanism renders some of these molecules good anti-cancer treatment if targeted correctly. The efficacy of intercalators is therefore of importance to the pharmaceutical industry. However due to forcefield inadequacy and the slow convergence of computational simulations, the application of well established binding free energy calculation methods to DNA-intercalator system to predict efficacy has been low in number compared to protein-ligand studies. Here we apply the three main methods to predicting efficacy via computational methods to DNA intercalator systems comparing results to experiment. We found that docking methods are capable to distinguish between intercalators that have different scaffold structures, MMPBSA type simulations can correctly rank a congeneric series of intercalators, and formally exact methods predict the binding affinity of intercalators with root mean squared error of 0.41 kcal/mol. The correct preparation of the models was also important, and to this end we developed computational tools to automate the correct setup stages. With an automated setup and deployment tool and running our protocols we think will start to probe a wide range of intercalators to investigate their interaction and efficacy with DNA.

\section{Introduction}


\input{methods}

\input{results}

\input{conclusion}

%\bibliography{mybib}
%\bibliographystyle{plain}

\end{document}